%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Riley}{Annis}{
\href{mailto:rileyannis@gmail.com}{rileyannis@gmail.com} | (269) 369-2726
\\2575 Bell Circle, Stevensville, MI 49127}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Michigan State University}
\descript{MS in Computer Science}
\location{Expected May 2019 | East Lansing, MI}
College of Engineering\\
Specialization in Theory of Computation\\
\sectionsep

\subsection{Michigan State University}
\descript{BS in Computer Science}
\location{Expected May 2018 | East Lansing, MI}
College of Engineering\\
Honors College\\
\location{Cum. GPA: 3.79 / 4.0}
\location{Major GPA: 3.91 / 4.0}
\sectionsep

\subsection{Michigan State University}
\descript{BS in Mathematics}
\location{Expected May 2018 | East Lansing, MI}
College of Natural Science\\
Honors College\\
\location{Cum. GPA: 3.79 / 4.0}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
\location{Completed}
Design and Theory of Algorithms\\
\location{In Progress}
Artificial Intelligence\\
Machine Learning\\
Neural Networks\\
Computer and Network Security\\
\sectionsep

\subsection{Undergraduate}
Translation of Programming Languages\\
Computer Networks\\
Logic and its Metatheory\\
Discrete Mathematics\\
Honors Abstract Algebra\\
Honors Real Analysis\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Programming}
\location{Proficient}
C++ \textbullet{} C \textbullet{} Python \textbullet{} Assembly\\
\location{Familiar}
C\# \textbullet{} .NET \textbullet{} Qt \textbullet{} HTML \textbullet{} CSS \textbullet{} \LaTeX\\
\location{Passing Knowledge}
Haskell \textbullet{} Java \textbullet{} JavaScript \textbullet{} XML\\
R \textbullet{} Visual Basic
\sectionsep
\subsection{Technologies}
Windows \textbullet{} Linux \textbullet{} Git \textbullet{} Bash

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Michigan State University}
\descript{| Graduate Assistant}
\location{Aug 2017 - Present | East Lansing, MI}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Currently working as a teaching assistant for CSE 450, Translation of Programming Languages (Compilers).
\item Responsibilities include answering student questions and providing feedback on course structure.
\end{tightemize}
\sectionsep

\runsubsection{Epic}
\descript{| Software Development Intern}
\location{May 2017 - Aug 2017 | Verona, WI}
\begin{tightemize}
\item Gained experience in a corporate environment, including work in C\# and .NET.
\item Led the research, design, and implementation of a novel project set to be added to a future release of Epic software.
\end{tightemize}
\sectionsep

\runsubsection{Michigan State University}
\descript{| Teaching Assistant for CSE 231}
\location{Aug 2016 - May 2017 | East Lansing, MI}
\begin{tightemize}
\item Ran lab sessions and worked helproom hours for Intro to Programming I (Python).
\item Utilized past leadership and teaching experience to instruct new computer science students.
\item Wrote two new projects with a focus on classes for future use in the course.
\end{tightemize}
\sectionsep

\runsubsection{Michigan State University}
\descript{| Teaching Assistant for MTH 110}
\location{Aug 2015 - May 2016 | East Lansing, MI}
\begin{tightemize}
\item Led recitation for Finite Mathematics and Elements of College Algebra.
\item Developed leadership and communication skills through assisting in undergraduate mathematics instruction.
\item Worked in the Math Learning Center tutoring courses from college algebra up through calculus.
\end{tightemize}
\sectionsep

\runsubsection{Michigan State University}
\descript{| Professorial Assistant}
\location{Aug 2014 – May 2016 | East Lansing, MI}
\begin{tightemize}
\item Worked in the MSU Digital Evolution Lab (devolab) under Dr. Charles Ofria.
\item Lead work on a research project in genetic algorithms and evolutionary computation.
\item Gained valuable experience in the academic research process.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards}

\begin{tabular}{rll}
Apr 2017 & 2\textsuperscript{nd} Place Team & Chicago Google Games hosted by Google\\
Oct 2016 & 1\textsuperscript{st} Place Team & Atomic Games hosted by Atomic Object\\
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Leadership
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Leadership} 

\begin{tabular}{rll}
Since Aug 2017 & UG Rep & MSU CSE Department Advisory Committee\\
Since Jan 2017 & Treasurer & Association for Computing Machinery at MSU\\
Since Aug 2016 & President & MSU Parkour and Freerunning Club\\
2010 - 2014 & Captain & First Robotics Comptetion Team 3452
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Societies} 

\begin{tabular}{rll}
Since Apr 2016 & Top 7.5 percentile & The Honor Society of Phi Kappa Phi\\
Since Apr 2016 & Top 12.5 percentile & Tau Beta Pi Engineering Honor Society\\
\end{tabular}
\sectionsep

\end{minipage} 
\end{document}