%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Riley}{Annis}{
\href{mailto:rileyannis@gmail.com}{rileyannis@gmail.com} | (269) 369-2726
\\2575 Bell Circle, Stevensville, MI 49127}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.33\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education} 

\subsection{Michigan State University}
\descript{MS in Computer Science}
\location{Expected May 2019 | East Lansing, MI}
College of Engineering\\
Specialization in Theory of Computation\\
\location{Cum. GPA: 4.0 / 4.0}
\sectionsep

\subsection{Michigan State University}
\descript{BS in Mathematics}
\location{Expected Dec 2018 | East Lansing, MI}
College of Natural Science\\
Honors College\\
\location{Cum. GPA: 3.79 / 4.0}
\sectionsep

\subsection{Michigan State University}
\descript{BS in Computer Science}
\location{Expected May 2018 | East Lansing, MI}
College of Engineering\\
Honors College\\
\location{Cum. GPA: 3.79 / 4.0}
\location{Major GPA: 3.88 / 4.0} % 147.5 / 38
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links} 
Github:// \href{https://github.com/rileyannis}{\custombold{rileyannis}} \\
LinkedIn://  \href{https://www.linkedin.com/in/rileyannis}{\custombold{rileyannis}} \\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
Design and Theory of Algorithms\\
Algorithmic Graph Theory\\
Artificial Intelligence\\
Machine Learning\\
Artificial Neural Networks\\
Pattern Recognition and Analysis\\
Natural Language Processing\\
Computer and Network Security\\
\sectionsep

\subsection{Undergraduate}
Algorithm Engineering\\
Translation of Prog. Languages\\
Organization of Prog. Languages\\
Computability and Languages\\
Computer Networks\\
Database Systems\\
Logic and its Metatheory\\
Discrete Mathematics\\
Honors Abstract Algebra\\
Honors Real Analysis\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SOCIETIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Societies} 
Tau Beta Pi Engineering Honor Society\\
The Honor Society of Phi Kappa Phi\\
\sectionsep


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage} 
\hfill
\begin{minipage}[t]{0.66\textwidth} 

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}

\runsubsection{Michigan State University}
\descript{| Graduate Assistant}
\location{Aug 2017 - Present | East Lansing, MI}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Currently working as a teaching assistant for CSE 431, Algorithm Engineering.
\item Previously worked as a teaching assistant for CSE 450, Translation of Programming Languages (Compilers).
\item Responsibilities include working office hours, answering student questions, grading assignments, and providing feedback on course structure.
\end{tightemize}
\sectionsep

\runsubsection{Epic}
\descript{| Software Development Intern}
\location{May 2017 - Aug 2017 | Verona, WI}
\begin{tightemize}
\item Gained experience in a corporate environment working with C\# and .NET.
\item Led the research, design, and implementation of a novel project set to be added to a future release of Epic software.
\end{tightemize}
\sectionsep

\runsubsection{Michigan State University}
\descript{| Teaching Assistant for CSE 231}
\location{Aug 2016 - May 2017 | East Lansing, MI}
\begin{tightemize}
\item Ran lab sessions and worked helproom hours for Intro to Programming I (Python).
\item Wrote two new projects with a focus on classes for future use in the course.
\end{tightemize}
\sectionsep

\runsubsection{Michigan State University}
\descript{| Teaching Assistant for MTH 110}
\location{Aug 2015 - May 2016 | East Lansing, MI}
\begin{tightemize}
\item Led recitation for Finite Mathematics and Elements of College Algebra.
\item Worked in the Math Learning Center tutoring courses from college algebra up through calculus.
\end{tightemize}
\sectionsep

\runsubsection{Michigan State University}
\descript{| Professorial Assistant}
\location{Aug 2014 – May 2016 | East Lansing, MI}
\begin{tightemize}
\item Worked in the MSU Digital Evolution Lab (devolab) under Dr. Charles Ofria.
\item Lead work on a research project involving genetic algorithms and evolutionary computation using Python.
\end{tightemize}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
%\subsection{Programming}
\location{Proficient}
Python \textbullet{} C++ \textbullet{} C \textbullet{} Assembly\\
\location{Familiar}
C\# \textbullet{} Java \textbullet{} JavaScript \textbullet{} Haskell \textbullet{} Rust \textbullet{}
Scala \textbullet{} Clojure \textbullet{} Erlang \textbullet{} SQL \textbullet{} Bash\\
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards}

\begin{tabular}{rll}
Oct 2017 & Completed & Google foo.bar Challenge\\
Oct 2017 & 1\textsuperscript{st} Place Team & 2017 MSU Google Games hosted by Google\\
Apr 2017 & 2\textsuperscript{nd} Place Team & 2017 Chicago Google Games hosted by Google\\
Oct 2016 & 1\textsuperscript{st} Place Team & 2016 Atomic Games hosted by Atomic Object\\
\end{tabular}
\sectionsep

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     Leadership
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Leadership} 

\begin{tabular}{rll}
Aug 2017 - May 2018 & UG Rep. & MSU CSE Department Advisory Committee\\
Aug 2016 - May 2018 & President & MSU Parkour and Freerunning Club\\
Sept 2017 - Jan 2018 & Swag Coord. & Spartahack IV Executive Board\\
Jan 2017 - Dec 2017 & Treasurer & Association for Computing Machinery at MSU\\
Sept 2010 - May 2014 & Captain & First Robotics Competition Team 3452\\
\end{tabular}
\sectionsep

\end{minipage} 
\end{document}